Survival Compass

### 2024-04-16 paper/paper.qmd
Graphs in data section are all done! Whoop Whoop! Now need to finish writing data section.

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-bills
#| fig-cap: four

@@

ggplot(pathologic_stage_counts, aes(x = pathologic_stage, y = percentage)) +
  geom_bar(stat = "identity", fill = "lightpink") +
  labs(title = "Percentage of Patients by Pathologic Stage",
       x = "Pathologic Stage",
       y = "Percentage") +
  theme_minimal() +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )

@@

ggplot(presence_of_distant_metastasis_counts, aes(x = presence_of_distant_metastasis, y = percentage)) +
  geom_bar(stat = "identity", fill = "gold") +
  labs(title = "Percentage of Patients by Presence of Distant Metastasis",
       x = "Presence of Distant Metastasis",
       y = "Percentage") +
  theme_minimal() +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )

@@

ggplot(lymph_node_involvement_counts, aes(x = lymph_node_involvement, y = percentage)) +
  geom_bar(stat = "identity", fill = "cyan") +
  labs(title = "Percentage of Patients by Lymph Node Involvement",
       x = "Lymph Node Involvement",
       y = "Percentage") +
  theme_minimal() +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )

@@

ggplot(tumor_size_counts, aes(x = tumor_size, y = percentage)) +
  geom_bar(stat = "identity", fill = "purple") +
  labs(title = "Percentage of Patients by Tumor Size",
       x = "Tumor Size",
       y = "Percentage") +
  theme_minimal() +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )

@@

Talk more about it.

>>>>

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: Figure 2
#| fig-cap: ADD FIGURE 2 CAPTION HERE 
#| fig-title: "Percentage of Lung Cancer Patients by:"

# install.packages("patchwork")

# load packages
library(ggplot2)
library(dplyr)
library(showtext)
library(arrow)
library(patchwork)

@@

@@

# Define a minimum height for the bars
min_bar_height <- 0.1  # Adjust as needed based on visibility preference

@@

@@

# Create subplots for all four plots
plots <- list(
  ggplot(pathologic_stage_counts, aes(x = pathologic_stage, y = percentage)) +
    geom_bar(stat = "identity", fill = "lightpink") +
    labs(title = "Pathologic Stage",
         x = "",
         y = "Percentage") +
    theme_minimal() +
    theme(
      text = element_text(family = "patrick"), # Set font to Patrick Hand
      axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis labels by 45 degrees
    ) +
    scale_y_continuous(breaks = seq(0, max(pathologic_stage_counts$percentage), by = 5)),

   ggplot(presence_of_distant_metastasis_counts, aes(x = presence_of_distant_metastasis, y = percentage)) +
    geom_bar(stat = "identity", fill = "gold") +
    labs(title = "Presence of Distant Metastasis",
         x = "",
         y = "") +  # Remove y-axis label 
    theme_minimal() +
    theme(
      text = element_text(family = "patrick"), # Set font to Patrick Hand
      axis.title.y = element_blank(), # Remove y-axis title
    ),

   ggplot(lymph_node_involvement_counts, aes(x = lymph_node_involvement, y = percentage)) +
    geom_bar(stat = "identity", fill = "cyan") +
    labs(title = "Lymph Node Involvement",
         x = "",
         y = "Percentage") +  # Keep y-axis label for this plot
    theme_minimal() +
    theme(
      text = element_text(family = "patrick") # Set font to Patrick Hand
    ) +
    scale_y_continuous(breaks = seq(0, max(lymph_node_involvement_counts$percentage), by = 10)),

  ggplot(tumor_size_counts, aes(x = tumor_size, y = percentage)) +
    geom_bar(stat = "identity", fill = "purple") +
    labs(title = "Tumor Size",
         x = "",
         y = "") +  # Remove y-axis label 
    theme_minimal() +
    theme(
      text = element_text(family = "patrick"), # Set font to Patrick Hand
      axis.title.y = element_blank() # Remove y-axis title
    )
)

# Combine plots using patchwork and largen the dimensions
plots_combined <- wrap_plots(plots, ncol = 2, height = 12, width = 14)

# Print combined plots
plots_combined

@@
